---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
suppressPackageStartupMessages({
  library(dplyr)
  library(rlang)
  library(gt)
  
  library(anon)
})
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

anon
==============================================================================



<!-- badges: start -->
![](https://img.shields.io/badge/cool-useless-green.svg)
![](https://img.shields.io/badge/status-rough-red.svg)
<!-- badges: end -->


The `anon` package provides two functions to help define succinct anonymous functions (also called *lambdas*).  

Features
-------------------------------------------------------------------------------

`anon` provides two user-facing functions:

1. `lambda()` for easily and compactly creating 
lambda expressions in R, while being broadly compatible with a number of existing
lambda syntaxes.  This function is also aliased to `L()` for the sake of brevity.
2. `patch_purrr_mapper()` to patch `purrr` to allow `anon` to convert formulas to functions instead of `rlang::as_function()`. Using `anon` to convert formulas-to-functions enables:
    * automatic argument extraction (rather than forcing the arguments to be `.x` and `.y`)
    * explicit arguments through the use of 2 sided formulas i.e. the formal arguments are extracted from 
    the expression on the LHS of a two-sided formula e.g. `a:b ~ a + b + 1` becomes `function(a, b) {a + b + 1}`


Installation
-------------------------------------------------------------------------------

You can install `anon` from [github](https://github.com/coolbutuseless/anon) with:

``` r
remotes::install_github("coolbutuseless/anon")
```

Example use of `lambda()`/`L()` for creating anonymous functions
-------------------------------------------------------------------------------

The following calls all create the same anonymous function:

* `function(x, y) x + y`
* `L(.x + .y)`
* `L(x + y)`
* `L(~x + y)`
* `L(x, y, x + y)`
* `L(x, y ~ x + y)`
* `L(x, y, ~x + y)`
* `L(x:y ~ x + y)`


Example use of `patch_purrr_mapper()` to enable extended functionality for lambdas in `purrr`
-------------------------------------------------------------------------------

By running `patch_purrr_mapper()` an extra S3 method is added for `purrr::as_mapper()` i.e.
`as_mapper.formula()`.  

By doing so, any *formula-used-as-function* in `purrr`
will be passed to `anon::as_function_formula()` which allows for more expressiveness 
than `rlang::as_function()`. i.e.

1. Can use any name for the variables, not just `.x` and `.y`
2. Can set explicit formal arguments (by specifying the LHS of the formula)
3. If no explicit formal arguments are given, then all variable names on the RHS of the
formula are used as formal arguments. The order of the formal arguments is the same 
as the order of appearance of the variables.
4. If `.x` or `.y` appear on the RHS and no explicit formal arguments are given on the LHS, 
then they are used as the first formal arguments (regardless of the order in which they appear on the RHS)
5. You can use `.` as a stand-in for the first argument.

```{r, message=FALSE, warning=FALSE}
library(purrr)
anon::patch_purrr_mapper()

z <- 10L

map_int(1:3, ~. + 1L)

map_int(1:3, ~.x + 1L)

map_int(1:3, ~ value + 1L)

map_int(1:3, val ~ val + 1L)

map_int(1:3, val ~ val + z)

map2_dbl(1:3, 4:6, ~ .x / .y)

map2_dbl(1:3, 4:6, ~ a / b)

map2_dbl(1:3, 4:6, ~ b / a)

map2_dbl(1:3, 4:6, b:a ~ a / b)

pmap_int(list(1:2, 3:4, 5:6, 7:8), ~a * b * c * d)
```









